\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-21 syntactic-example.tex
comments

We provide one example in its surface syntax as pseudocode, and their
meta-theory encoding. This example is computing the predecessor of a
mundane natural number, but we split the inductive definition into two
parts and making "O" and "S" standing alone.
"pred" will map $S~n \mapsto (n, S~n)$ and $O \mapsto (O, O)$, and thus a predecessor.

@@

  (* sig₄₁, inh₅, sl₄₁ *)
 Inherits k. 
 (* inh₆ *)
EndFamily.
    \end{minted}
  \end{minipage}
  \caption{Demonstrating Pseudo-Code}
\end{figure}

>>>>

We provide one example in its surface syntax as pseudocode, and their
meta-theory encoding. This example is computing the predecessor of a
mundane natural number, but we split the inductive definition into two
parts and making "O" and "S" standing alone.
"pred" will map $S~n \mapsto (n, S~n)$ and $O \mapsto (O, O)$, and thus a predecessor.\YZ{
  Using family polymorphism for adding  a successor constructor is unnatural.
  I suggest simply renaming the constructors and not mentioning the correspondence to natural numbers.
}

@@

  (* sig₄₁, inh₅, sl₄₁ *)
 Inherits k. 
 (* inh₆ *)
EndFamily.
    \end{minted}
  \end{minipage}\YZ{This figure needs updating; it should use the same syntax as in §3.}\YZreply{Also, this figure should contain an example of accessing a field outside its family.}
  \caption{Demonstrating Pseudo-Code}
\end{figure}
